%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
	\cventry
	{2022 Fieldwork} % Job title
	{July 2022} % Date(s)
	{RAVEN, NASA, JPL} % Organisation
	{Dreki \& Holuhraun, Icelandic Highlands} % Location
	{
	\begin{cvitems}
		\item Collected terrain data from a drone-based stereo depth camera over Holuhraun lava flow.
		\item Executed manual and autonomous drone missions in the field.
		\item Assisted in collection of LIDAR terrain data and doppler LIDAR dust data from drone propeller wash.
		\item Assisted in collection of hyperspectral data describing chemical makeup of various locations of interest.
		\item Cooperated with interdisciplinary team of geologists and planetary scientists to set up and tear down camp, long-range WiFi connection.
	\end{cvitems}
	}  

	\cventry
	{2021 Fieldwork} % Job title
	{July 2021} % Date(s)
	{RAVEN} % Organisation
	{Fagradalsfjall Volcanic Eruption} % Location
	{
	\begin{cvitems}
		\item Assembled heavy-lift drone with thermal camera (FLIR A615), collected thermal data over active lava flow
		\item Featured on BBC Click: \url{https://www.bbc.co.uk/programmes/p09r8nzv}
	\end{cvitems}
	}  

	\cventry
	{IT Analyst, Integration Development} % Job title
	{February 2017 - August 2018} % Date(s)
	{LSU Information Technology Services} % Organisation
	{Baton Rouge, United States} % Location
	{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Created, and managed production deployment of reports and integrations in Workday and other platforms.}
		\item {Administered and maintained integration platform servers.}
		\item {Communicated with clients and team for requirements and troubleshooting.}
		\item {Created and optimized simple to complex SQL queries and tables.}
	\end{cvitems}
	}  

	\cventry
	{System Administration Team Member} % Job title
	{January 2016 - December 2016} % Date(s)
	{LSU High Performance Computing Services} % Organisation
	{Baton Rouge, United States} % Location
	{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Managed computational loads on 6 RHEL supercomputing clusters.}
		\item {Performed cluster-wide software upgrades and hardware repairs.}
		\item {Troubleshot hardware issues and carried out repairs.}
	\end{cvitems}
	}

%---------------------------------------------------------
\end{cventries}
